---
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readr)
library(lubridate)
library(tidyverse)
library(stringr)
library(ggpubr)
library(rstatix)
library(latex2exp)

dat <- read_csv("~/R/R_Projects/DengueAI/RawData/_DATA_2022-12-01_1125.csv")
dat1 <- read_csv("~/R/R_Projects/DengueAI/RawData/_DATA_LABELS_2022-12-01_1122.csv")
dat2 <- read_csv("~/R/R_Projects/DengueAI/RawData/CoDEN_for_Peter_20201002.csv")

theme_set(theme_bw())

#### mean_ci function
new_mean_ci <- function(vector, alpha = 0.05, na.rm = T){
  if(na.rm){
  n_vector <- vector[!is.na(vector)]
  }else{
    n_vector <- vector
  }
  
  sample.mean <- mean(n_vector)
  sample.n <- length(n_vector)
  sample.sd <- sd(n_vector)
  sample.se <- sample.sd/sqrt(sample.n)
  
  degrees.freedom = sample.n - 1
  t.score = qt(p=alpha/2, df=degrees.freedom,lower.tail=F)
  
  margin.error <- t.score * sample.se
  lower.bound <- sample.mean - margin.error
  upper.bound <- sample.mean + margin.error
  
  return(cbind(c(sample.mean,lower.bound,upper.bound)))
}

# Format Dx and Day0
DX_Day0 <- dat1[!is.na(dat1$`Final Dx`),c("SNO:","Final Dx","Final D0")]
DX_Day0$simple_Dx <- "DHF"
DX_Day0$simple_Dx[which(DX_Day0$`Final Dx` == "Not dengue")] <- "OFI"
DX_Day0$simple_Dx[which(DX_Day0$`Final Dx` == "DF")] <- "DF"
DX_Day0$final_day0 <- ymd(DX_Day0$`Final D0`)
DX_Day0$`Final Dx` <- DX_Day0$`Final D0` <- NULL

dat <- merge(dat,DX_Day0, by.x = "sno",by.y="SNO:")

# Format Site
dat$site <- factor((substr(dat$sno,3,3)),levels = 1:2, labels = c("KK","SK"))

# Format to_day0
dat$date <- ymd(dat$date_d04)
dat$to_day0 <- dat$date - dat$final_day0

# Format study day
dat$study_day <- as.numeric(str_match(dat$redcap_event_name, ".?study_day_([0-9])_arm_1")[,2])

# Format fever day
fever <- dat[!is.na(dat$fever_date), c("sno","fever_date")]
fever$f_date <- ymd(fever$fever_date)
dat <- merge(dat,fever, by = "sno", all.x = T)
dat$fever_day <- dat$date - dat$f_date

# Format platelet
dat$log.platelet <- log10(1+dat$platelet_d05*10^3)

# Format WBC
dat$log.wbc <- log10(1+dat$wbc_d05*10^3)

# Format PMN
dat$abs_pmn <- ((dat$pmn * dat$wbc_d05)/100)

# Format BAND
dat$abs_band <- ((dat$band * dat$wbc_d05)/100)

# Format LYMP
dat$abs_lymp <- ((dat$lymp * dat$wbc_d05)/100)

# Format ATYP
dat$abs_atyp <- ((dat$atyp * dat$wbc_d05)/100)

# Format MONO
dat$abs_mono <- ((dat$mono * dat$wbc_d05)/100)

# Format BASO
dat$abs_baso <- ((dat$baso * dat$wbc_d05)/100)

# Format EOSIN
dat$abs_eosin <- ((dat$eosin * dat$wbc_d05)/100)

# Format LFT protein
dat$log.prot <- log10(1+dat$lft_protein)

# Format LFT albumin
dat$log.alb <- log10(1+dat$lft_albumin)

# Format LFT AST
dat$log.ast <- log10(1+dat$lft_ast)

# Format LFT ALT
dat$log.alt <- log10(1+dat$lft_alt)

# Format Fluid retention
dat$fluid_ret <- rowSums(dat[,c("intake1","intake2","intake3")], na.rm = T) - rowSums(dat[,c("output1","output2","output3")], na.rm = T)

dat <- dat[which(dat$simple_Dx != "OFI"),]
dat$simple_Dx <- factor(dat$simple_Dx, levels = c("DHF","DF"), labels = c("DHF","Non-DHF"))

#### Use identical dataset as Peter's ####
dat <- dat[dat$sno %in% unique(dat2$d01_sno),]
#### Show <= 5 study day
dat <- dat[which(dat$study_day <= 5),]
### Jitter study day
dat$jstudy_day <- dat$study_day + 0.1
dat$jstudy_day[dat$simple_Dx == "Non-DHF"] <- dat$study_day[dat$simple_Dx == "Non-DHF"] - 0.1
```


```{r platelet, echo=FALSE, warning=FALSE, fig.width=8,fig.height=8}
meandat <- aggregate(platelet_d05 ~ simple_Dx + study_day, dat, new_mean_ci)
meandat$mean <- meandat[,3][,1]
meandat$low <- meandat[,3][,2]
meandat$up <- meandat[,3][,3]

gA <- ggplot(dat, aes(dat, x = jstudy_day, col = simple_Dx, y = platelet_d05))+
  geom_jitter(width = 0.07, shape = 1)+
  xlab("Study day")+
  ylab(TeX("Platelet count (x 1000 cells/$\\mu$l)"))+
  scale_color_manual(name = "Diagnosis", values = c("#EFC000FF","#0073C2FF"))+
  coord_cartesian(ylim = c(0,500))+
  theme(legend.position = "top")

gB <- ggplot(meandat,aes(x = study_day, col = simple_Dx))+
  geom_line(aes(y=mean,group=simple_Dx)) +
  geom_ribbon(aes(ymin = low,ymax=up,fill=simple_Dx), alpha = 0.3, col = NA)+
  xlab("Study day")+
  ylab(TeX("Platelet count (x 1000 cells/$\\mu$l)"))+
  scale_color_manual(name = "Diagnosis", values = c("#EFC000FF","#0073C2FF"))+
  scale_fill_manual(name = "Diagnosis", values = c("#EFC000FF","#0073C2FF"))+
  coord_cartesian(ylim = c(0,500))+
  theme(legend.position = "top")

gC <- ggplot(meandat,aes(x = study_day, col = simple_Dx))+
  geom_line(aes(y=mean,group=simple_Dx)) +
  geom_ribbon(aes(ymin = low,ymax=up,fill=simple_Dx), alpha = 0.3, col = NA)+
  xlab("Study day")+
  ylab(TeX("Platelet count (x 1000 cells/$\\mu$l)"))+
  scale_color_manual(name = "Diagnosis", values =  c("#EFC000FF","#0073C2FF"))+
  scale_fill_manual(name = "Diagnosis", values = c("#EFC000FF","#0073C2FF"))+
  #coord_cartesian(ylim = c(0,500))+
  theme(legend.position = "top")


g <- ggarrange(gA,gB,gC,ncol = 2,nrow = 2, labels = c("A","B","C"))
print(g)
ggsave(filename = "../Plots/Supplement_platelet_count.tiff",width=8,height = 8,units = "in",dpi=300)
ggsave(filename = "../Plots/Supplement_platelet_count.eps",width=8,height = 8,units = "in", device=cairo_ps)
```

**Fig. 1:** Time course of `Platelet count` variable from study day one to five in two groups (DHF and Non-DHF).  The data are shown as raw values (A) and means by group by study day (B) with the shaded areas representing 95% confident intervals of the means. The mean values (B) are also zoomed in to show the difference and trajectories two groups (C).

\newpage

```{r hct_lab, echo=FALSE, warning=FALSE, fig.width=8,fig.height=8}
meandat <- aggregate(hct_d05 ~ simple_Dx + study_day, dat, new_mean_ci)
meandat$mean <- meandat[,3][,1]
meandat$low <- meandat[,3][,2]
meandat$up <- meandat[,3][,3]

gA <- ggplot(dat, aes(dat, x = jstudy_day, col = simple_Dx, y = hct_d05))+
  geom_jitter(width = 0.07, shape = 1)+
  xlab("Study day")+
  ylab(TeX("Hematocrit (%)"))+
  scale_color_manual(name = "Diagnosis", values = c("#EFC000FF","#0073C2FF"))+
  coord_cartesian(ylim = c(15,50))+
  theme(legend.position = "top")

gB <- ggplot(meandat,aes(x = study_day, col = simple_Dx))+
  geom_line(aes(y=mean,group=simple_Dx)) +
  geom_ribbon(aes(ymin = low,ymax=up,fill=simple_Dx), alpha = 0.3, col = NA)+
  xlab("Study day")+
  ylab(TeX("Hematocrit (%)"))+
  scale_color_manual(name = "Diagnosis", values = c("#EFC000FF","#0073C2FF"))+
  scale_fill_manual(name = "Diagnosis", values = c("#EFC000FF","#0073C2FF"))+
  coord_cartesian(ylim = c(15,50))+
  theme(legend.position = "top")

gC <- ggplot(meandat,aes(x = study_day, col = simple_Dx))+
  geom_line(aes(y=mean,group=simple_Dx)) +
  geom_ribbon(aes(ymin = low,ymax=up,fill=simple_Dx), alpha = 0.3, col = NA)+
  xlab("Study day")+
  ylab(TeX("Hematocrit (%)"))+
  scale_color_manual(name = "Diagnosis", values = c("#EFC000FF","#0073C2FF"))+
  scale_fill_manual(name = "Diagnosis", values = c("#EFC000FF","#0073C2FF"))+
  #coord_cartesian(ylim = c(15,50))+
  theme(legend.position = "top")

g <- ggarrange(gA,gB,gC,ncol = 2,nrow = 2, labels = c("A","B","C"))
print(g)
ggsave(plot = g, filename = "../Plots/Supplement_hematocrit.eps",width=8,height = 8,units = "in", device=cairo_ps)
```

**Fig. 2:** Time course of `Hematocrit` variable from study day one to five in two groups (DHF and Non-DHF).  The data are shown as raw values (A) and means by group by study day (B) with the shaded areas representing 95% confident intervals of the means. The mean values (B) are also zoomed in to show the difference and trajectories two groups (C).

\newpage

```{r WBC, echo=FALSE, warning=FALSE, fig.width=8,fig.height=8}
meandat <- aggregate(wbc_d05 ~ simple_Dx + study_day, dat, new_mean_ci)
meandat$mean <- meandat[,3][,1]
meandat$low <- meandat[,3][,2]
meandat$up <- meandat[,3][,3]

gA <- ggplot(dat, aes(dat, x = jstudy_day, col = simple_Dx, y = wbc_d05))+
  geom_jitter(width = 0.07, shape = 1)+
  xlab("Study day")+
  ylab(TeX("WBC (x 1000 cells/$\\mu$l)"))+
  scale_color_manual(name = "Diagnosis", values = c("#EFC000FF","#0073C2FF"))+
  coord_cartesian(ylim = c(0,40))+
  theme(legend.position = "top")

gB <- ggplot(meandat,aes(x = study_day, col = simple_Dx))+
  geom_line(aes(y=mean,group=simple_Dx)) +
  geom_ribbon(aes(ymin = low,ymax=up,fill=simple_Dx), alpha = 0.3, col = NA)+
  xlab("Study day")+
  ylab(TeX("WBC (x 1000 cells/$\\mu$l)"))+
  scale_color_manual(name = "Diagnosis", values = c("#EFC000FF","#0073C2FF"))+
  scale_fill_manual(name = "Diagnosis", values = c("#EFC000FF","#0073C2FF"))+
  coord_cartesian(ylim = c(0,40))+
  theme(legend.position = "top")

gC <- ggplot(meandat,aes(x = study_day, col = simple_Dx))+
  geom_line(aes(y=mean,group=simple_Dx)) +
  geom_ribbon(aes(ymin = low,ymax=up,fill=simple_Dx), alpha = 0.3, col = NA)+
  xlab("Study day")+
  ylab(TeX("WBC (x 1000 cells/$\\mu$l)"))+
  scale_color_manual(name = "Diagnosis", values = c("#EFC000FF","#0073C2FF"))+
  scale_fill_manual(name = "Diagnosis", values = c("#EFC000FF","#0073C2FF"))+
  #coord_cartesian(ylim = c(0,40))+
  theme(legend.position = "top")

g <- ggarrange(gA,gB,gC,nrow = 2,ncol=2, labels = c("A","B","C"))
print(g)

ggsave(plot = g, filename = "../Plots/Supplement_WBC.eps",width=8,height = 8,units = "in", device=cairo_ps)
```

**Fig. 3:** Time course of `WBC` (white blood cell) variable from study day one to five in two groups (DHF and Non-DHF).  The data are shown as raw values (A) and means by group by study day (B) with the shaded areas representing 95% confident intervals of the means. The mean values (B) are also zoomed in to show the difference and trajectories two groups (C).

\newpage

```{r PMN, echo=FALSE, warning=FALSE, fig.width=8,fig.height=8}
meandat <- aggregate(abs_pmn ~ simple_Dx + study_day, dat, new_mean_ci)
meandat$mean <- meandat[,3][,1]
meandat$low <- meandat[,3][,2]
meandat$up <- meandat[,3][,3]

gA <- ggplot(dat, aes(dat, x = jstudy_day, col = simple_Dx, y = abs_pmn))+
  geom_jitter(width = 0.07, shape = 1)+
  xlab("Study day")+
  ylab(TeX("Absolute PMN (x 1000 cells/$\\mu$l)"))+
  scale_color_manual(name = "Diagnosis", values = c("#EFC000FF","#0073C2FF"))+
  coord_cartesian(ylim = c(0,20))+
  theme(legend.position = "top")

gB <- ggplot(meandat,aes(x = study_day, col = simple_Dx))+
  geom_line(aes(y=mean,group=simple_Dx)) +
  geom_ribbon(aes(ymin = low,ymax=up,fill=simple_Dx), alpha = 0.3, col = NA)+
  xlab("Study day")+
  ylab(TeX("Absolute PMN (x 1000 cells/$\\mu$l)"))+
  scale_color_manual(name = "Diagnosis", values = c("#EFC000FF","#0073C2FF"))+
  scale_fill_manual(name = "Diagnosis", values = c("#EFC000FF","#0073C2FF"))+
  coord_cartesian(ylim = c(0,20))+
  theme(legend.position = "top")

gC <- ggplot(meandat,aes(x = study_day, col = simple_Dx))+
  geom_line(aes(y=mean,group=simple_Dx)) +
  geom_ribbon(aes(ymin = low,ymax=up,fill=simple_Dx), alpha = 0.3, col = NA)+
  xlab("Study day")+
  ylab(TeX("Absolute PMN (x 1000 cells/$\\mu$l)"))+
  scale_color_manual(name = "Diagnosis", values = c("#EFC000FF","#0073C2FF"))+
  scale_fill_manual(name = "Diagnosis", values = c("#EFC000FF","#0073C2FF"))+
  #coord_cartesian(ylim = c(0,20))+
  theme(legend.position = "top")

g <- ggarrange(gA,gB,gC,nrow = 2,ncol=2, labels = c("A","B","C"))
print(g)
ggsave(plot = g, filename = "../Plots/Supplement_PMN.eps",width=8,height = 8,units = "in", device=cairo_ps)
```

**Fig. 4:** Time course of `PMN` (polymorphonuclear neutrophil) variable from study day one to five in two groups (DHF and Non-DHF).  The data are shown as raw values (A) and means by group by study day (B) with the shaded areas representing 95% confident intervals of the means. The mean values (B) are also zoomed in to show the difference and trajectories two groups (C).

\newpage

```{r band, echo=FALSE, warning=FALSE, fig.width=8,fig.height=8}
meandat <- aggregate(abs_band ~ simple_Dx + study_day, dat, new_mean_ci)
meandat$mean <- meandat[,3][,1]
meandat$low <- meandat[,3][,2]
meandat$up <- meandat[,3][,3]

gA <- ggplot(dat, aes(dat, x = jstudy_day, col = simple_Dx, y = abs_band))+
  geom_jitter(width = 0.07, shape = 1)+
  xlab("Study day")+
  ylab(TeX("Absolute BAND (x 1000 cells/$\\mu$l)"))+
  scale_color_manual(name = "Diagnosis", values = c("#EFC000FF","#0073C2FF"))+
  coord_cartesian(ylim = c(0,2.5))+
  theme(legend.position = "top")

gB <- ggplot(meandat,aes(x = study_day, col = simple_Dx))+
  geom_line(aes(y=mean,group=simple_Dx)) +
  geom_ribbon(aes(ymin = low,ymax=up,fill=simple_Dx), alpha = 0.3, col = NA)+
  xlab("Study day")+
  ylab(TeX("Absolute BAND (x 1000 cells/$\\mu$l)"))+
  scale_color_manual(name = "Diagnosis", values = c("#EFC000FF","#0073C2FF"))+
  scale_fill_manual(name = "Diagnosis", values = c("#EFC000FF","#0073C2FF"))+
  coord_cartesian(ylim = c(0,2.5))+
  theme(legend.position = "top")

gC <- ggplot(meandat,aes(x = study_day, col = simple_Dx))+
  geom_line(aes(y=mean,group=simple_Dx)) +
  geom_ribbon(aes(ymin = low,ymax=up,fill=simple_Dx), alpha = 0.3, col = NA)+
  xlab("Study day")+
  ylab(TeX("Absolute BAND (x 1000 cells/$\\mu$l)"))+
  scale_color_manual(name = "Diagnosis", values = c("#EFC000FF","#0073C2FF"))+
  scale_fill_manual(name = "Diagnosis", values = c("#EFC000FF","#0073C2FF"))+
  #coord_cartesian(ylim = c(0,2.5))+
  theme(legend.position = "top")

g <- ggarrange(gA,gB,gC,nrow = 2,ncol=2, labels = c("A","B","C"))
print(g)

ggsave(plot = g, filename = "../Plots/Supplement_BAND.eps",width=8,height = 8,units = "in", device=cairo_ps)
```

**Fig. 5:** Time course of `BAND`  variable from study day one to five in two groups (DHF and Non-DHF).  The data are shown as raw values (A) and means by group by study day (B) with the shaded areas representing 95% confident intervals of the means. The mean values (B) are also zoomed in to show the difference and trajectories two groups (C).

\newpage

```{r lymp, echo=FALSE, warning=FALSE, fig.width=8,fig.height=8}
meandat <- aggregate(abs_lymp ~ simple_Dx + study_day, dat, new_mean_ci)
meandat$mean <- meandat[,3][,1]
meandat$low <- meandat[,3][,2]
meandat$up <- meandat[,3][,3]

gA <- ggplot(dat, aes(dat, x = jstudy_day, col = simple_Dx, y = abs_lymp))+
  geom_jitter(width = 0.07, shape = 1)+
  xlab("Study day")+
  ylab(TeX("Absolute LYMP (x 1000 cells/$\\mu$l)"))+
  scale_color_manual(name = "Diagnosis", values = c("#EFC000FF","#0073C2FF"))+
  coord_cartesian(ylim = c(0,20))+
  theme(legend.position = "top")

gB <- ggplot(meandat,aes(x = study_day, col = simple_Dx))+
  geom_line(aes(y=mean,group=simple_Dx)) +
  geom_ribbon(aes(ymin = low,ymax=up,fill=simple_Dx), alpha = 0.3, col = NA)+
  xlab("Study day")+
  ylab(TeX("Absolute LYMP (x 1000 cells/$\\mu$l)"))+
  scale_color_manual(name = "Diagnosis", values = c("#EFC000FF","#0073C2FF"))+
  scale_fill_manual(name = "Diagnosis", values = c("#EFC000FF","#0073C2FF"))+
  coord_cartesian(ylim = c(0,20))+
  theme(legend.position = "top")

gC <- ggplot(meandat,aes(x = study_day, col = simple_Dx))+
  geom_line(aes(y=mean,group=simple_Dx)) +
  geom_ribbon(aes(ymin = low,ymax=up,fill=simple_Dx), alpha = 0.3, col = NA)+
  xlab("Study day")+
  ylab(TeX("Absolute LYMP (x 1000 cells/$\\mu$l)"))+
  scale_color_manual(name = "Diagnosis", values = c("#EFC000FF","#0073C2FF"))+
  scale_fill_manual(name = "Diagnosis", values = c("#EFC000FF","#0073C2FF"))+
  #coord_cartesian(ylim = c(0,20))+
  theme(legend.position = "top")

g <- ggarrange(gA,gB,gC,nrow = 2,ncol=2, labels = c("A","B","C"))
print(g)
ggsave(plot = g, filename = "../Plots/Supplement_LYMP.eps",width=8,height = 8,units = "in", device=cairo_ps)
```

**Fig. 6:** Time course of `LYMP` (Lymphocyte)  variable from study day one to five in two groups (DHF and Non-DHF).  The data are shown as raw values (A) and means by group by study day (B) with the shaded areas representing 95% confident intervals of the means. The mean values (B) are also zoomed in to show the difference and trajectories two groups (C).


\newpage

```{r atyp, echo=FALSE, warning=FALSE, fig.width=8,fig.height=8}
meandat <- aggregate(abs_atyp ~ simple_Dx + study_day, dat, new_mean_ci)
meandat$mean <- meandat[,3][,1]
meandat$low <- meandat[,3][,2]
meandat$up <- meandat[,3][,3]

gA <- ggplot(dat, aes(dat, x = jstudy_day, col = simple_Dx, y = abs_atyp))+
  geom_jitter(width = 0.07, shape = 1)+
  xlab("Study day")+
  ylab(TeX("Absolute ATYP (x 1000 cells/$\\mu$l)"))+
  scale_color_manual(name = "Diagnosis", values = c("#EFC000FF","#0073C2FF"))+
  coord_cartesian(ylim = c(0,10))+
  theme(legend.position = "top")

gB <- ggplot(meandat,aes(x = study_day, col = simple_Dx))+
  geom_line(aes(y=mean,group=simple_Dx)) +
  geom_ribbon(aes(ymin = low,ymax=up,fill=simple_Dx), alpha = 0.3, col = NA)+
  xlab("Study day")+
  ylab(TeX("Absolute ATYP (x 1000 cells/$\\mu$l)"))+
  scale_color_manual(name = "Diagnosis", values = c("#EFC000FF","#0073C2FF"))+
  scale_fill_manual(name = "Diagnosis", values = c("#EFC000FF","#0073C2FF"))+
  coord_cartesian(ylim = c(0,10))+
  theme(legend.position = "top")

gC <- ggplot(meandat,aes(x = study_day, col = simple_Dx))+
  geom_line(aes(y=mean,group=simple_Dx)) +
  geom_ribbon(aes(ymin = low,ymax=up,fill=simple_Dx), alpha = 0.3, col = NA)+
  xlab("Study day")+
  ylab(TeX("Absolute ATYP (x 1000 cells/$\\mu$l)"))+
  scale_color_manual(name = "Diagnosis", values = c("#EFC000FF","#0073C2FF"))+
  scale_fill_manual(name = "Diagnosis", values = c("#EFC000FF","#0073C2FF"))+
  #coord_cartesian(ylim = c(0,10))+
  theme(legend.position = "top")

g <- ggarrange(gA,gB,gC,nrow = 2,ncol=2, labels = c("A","B","C"))
print(g)

ggsave(plot = g, filename = "../Plots/Supplement_ATYP.eps",width=8,height = 8,units = "in", device=cairo_ps)
```

**Fig. 7:** Time course of `ATYP` (Atypical lymphocyte)  variable from study day one to five in two groups (DHF and Non-DHF).  The data are shown as raw values (A) and means by group by study day (B) with the shaded areas representing 95% confident intervals of the means. The mean values (B) are also zoomed in to show the difference and trajectories two groups (C).

\newpage

```{r mono, echo=FALSE, warning=FALSE, fig.width=8,fig.height=8}
meandat <- aggregate(abs_mono ~ simple_Dx + study_day, dat, new_mean_ci)
meandat$mean <- meandat[,3][,1]
meandat$low <- meandat[,3][,2]
meandat$up <- meandat[,3][,3]

gA <- ggplot(dat, aes(dat, x = jstudy_day, col = simple_Dx, y = abs_mono))+
  geom_jitter(width = 0.07, shape = 1)+
  xlab("Study day")+
  ylab(TeX("Absolute MONO (x 1000 cells/$\\mu$l)"))+
  scale_color_manual(name = "Diagnosis", values = c("#EFC000FF","#0073C2FF"))+
  coord_cartesian(ylim = c(0,6))+
  theme(legend.position = "top")

gB <- ggplot(meandat,aes(x = study_day, col = simple_Dx))+
  geom_line(aes(y=mean,group=simple_Dx)) +
  geom_ribbon(aes(ymin = low,ymax=up,fill=simple_Dx), alpha = 0.3, col = NA)+
  xlab("Study day")+
  ylab(TeX("Absolute MONO (x 1000 cells/$\\mu$l)"))+
  scale_color_manual(name = "Diagnosis", values = c("#EFC000FF","#0073C2FF"))+
  scale_fill_manual(name = "Diagnosis", values = c("#EFC000FF","#0073C2FF"))+
  coord_cartesian(ylim = c(0,6))+
  theme(legend.position = "top")

gC <- ggplot(meandat,aes(x = study_day, col = simple_Dx))+
  geom_line(aes(y=mean,group=simple_Dx)) +
  geom_ribbon(aes(ymin = low,ymax=up,fill=simple_Dx), alpha = 0.3, col = NA)+
  xlab("Study day")+
  ylab(TeX("Absolute MONO (x 1000 cells/$\\mu$l)"))+
  scale_color_manual(name = "Diagnosis", values = c("#EFC000FF","#0073C2FF"))+
  scale_fill_manual(name = "Diagnosis", values = c("#EFC000FF","#0073C2FF"))+
  #coord_cartesian(ylim = c(0,6))+
  theme(legend.position = "top")

g <- ggarrange(gA,gB,gC,nrow = 2,ncol=2, labels = c("A","B","C"))
print(g)

ggsave(plot = g, filename = "../Plots/Supplement_MONO.eps",width=8,height = 8,units = "in", device=cairo_ps)
```

**Fig. 8:** Time course of `MONO` (Monocyte)  variable from study day one to five in two groups (DHF and Non-DHF).  The data are shown as raw values (A) and means by group by study day (B) with the shaded areas representing 95% confident intervals of the means. The mean values (B) are also zoomed in to show the difference and trajectories two groups (C).

\newpage

```{r baso, echo=FALSE, warning=FALSE, fig.width=8,fig.height=8}
meandat <- aggregate(abs_baso ~ simple_Dx + study_day, dat, new_mean_ci)
meandat$mean <- meandat[,3][,1]
meandat$low <- meandat[,3][,2]
meandat$up <- meandat[,3][,3]

gA <- ggplot(dat, aes(dat, x = jstudy_day, col = simple_Dx, y = abs_baso))+
  geom_jitter(width = 0.07, shape = 1)+
  xlab("Study day")+
  ylab(TeX("Absolute BASO (x 1000 cells/$\\mu$l)"))+
  scale_color_manual(name = "Diagnosis", values = c("#EFC000FF","#0073C2FF"))+
  coord_cartesian(ylim = c(0,0.6))+
  theme(legend.position = "top")

gB <- ggplot(meandat,aes(x = study_day, col = simple_Dx))+
  geom_line(aes(y=mean,group=simple_Dx)) +
  geom_ribbon(aes(ymin = low,ymax=up,fill=simple_Dx), alpha = 0.3, col = NA)+
  xlab("Study day")+
  ylab(TeX("Absolute BASO (x 1000 cells/$\\mu$l)"))+
  scale_color_manual(name = "Diagnosis", values = c("#EFC000FF","#0073C2FF"))+
  scale_fill_manual(name = "Diagnosis", values = c("#EFC000FF","#0073C2FF"))+
  coord_cartesian(ylim = c(0,0.6))+
  theme(legend.position = "top")

gC <- ggplot(meandat,aes(x = study_day, col = simple_Dx))+
  geom_line(aes(y=mean,group=simple_Dx)) +
  geom_ribbon(aes(ymin = low,ymax=up,fill=simple_Dx), alpha = 0.3, col = NA)+
  xlab("Study day")+
  ylab(TeX("Absolute BASO (x 1000 cells/$\\mu$l)"))+
  scale_color_manual(name = "Diagnosis", values = c("#EFC000FF","#0073C2FF"))+
  scale_fill_manual(name = "Diagnosis", values = c("#EFC000FF","#0073C2FF"))+
  #coord_cartesian(ylim = c(0,0.6))+
  theme(legend.position = "top")

g <- ggarrange(gA,gB,gC,nrow = 2,ncol=2, labels = c("A","B","C"))
print(g)

ggsave(plot = g, filename = "../Plots/Supplement_BASO.eps",width=8,height = 8,units = "in", device=cairo_ps)
```

**Fig. 9:** Time course of `BASO` (Basophil)  variable from study day one to five in two groups (DHF and Non-DHF).  The data are shown as raw values (A) and means by group by study day (B) with the shaded areas representing 95% confident intervals of the means. The mean values (B) are also zoomed in to show the difference and trajectories two groups (C).

\newpage

```{r eosin, echo=FALSE, warning=FALSE, fig.width=8,fig.height=8}
meandat <- aggregate(abs_eosin ~ simple_Dx + study_day, dat, new_mean_ci)
meandat$mean <- meandat[,3][,1]
meandat$low <- meandat[,3][,2]
meandat$up <- meandat[,3][,3]

gA <- ggplot(dat, aes(dat, x = jstudy_day, col = simple_Dx, y = abs_eosin))+
  geom_jitter(width = 0.07, shape = 1)+
  xlab("Study day")+
  ylab(TeX("Absolute EOSIN (x 1000 cells/$\\mu$l)"))+
  scale_color_manual(name = "Diagnosis", values = c("#EFC000FF","#0073C2FF"))+
  coord_cartesian(ylim = c(0,5))+
  theme(legend.position = "top")

gB <- ggplot(meandat,aes(x = study_day, col = simple_Dx))+
  geom_line(aes(y=mean,group=simple_Dx)) +
  geom_ribbon(aes(ymin = low,ymax=up,fill=simple_Dx), alpha = 0.3, col = NA)+
  xlab("Study day")+
  ylab(TeX("Absolute EOSIN (x 1000 cells/$\\mu$l)"))+
  scale_color_manual(name = "Diagnosis", values = c("#EFC000FF","#0073C2FF"))+
  scale_fill_manual(name = "Diagnosis", values = c("#EFC000FF","#0073C2FF"))+
  coord_cartesian(ylim = c(0,5))+
  theme(legend.position = "top")

gC <- ggplot(meandat,aes(x = study_day, col = simple_Dx))+
  geom_line(aes(y=mean,group=simple_Dx)) +
  geom_ribbon(aes(ymin = low,ymax=up,fill=simple_Dx), alpha = 0.3, col = NA)+
  xlab("Study day")+
  ylab(TeX("Absolute EOSIN (x 1000 cells/$\\mu$l)"))+
  scale_color_manual(name = "Diagnosis", values = c("#EFC000FF","#0073C2FF"))+
  scale_fill_manual(name = "Diagnosis", values = c("#EFC000FF","#0073C2FF"))+
  #coord_cartesian(ylim = c(0,5))+
  theme(legend.position = "top")

g <- ggarrange(gA,gB,gC,nrow = 2,ncol=2, labels = c("A","B","C"))
print(g)
ggsave(plot = g, filename = "../Plots/Supplement_EOSIN.eps",width=8,height = 8,units = "in", device=cairo_ps)
```

**Fig. 10:** Time course of `EOSIN` (Eosinophil)  variable from study day one to five in two groups (DHF and Non-DHF).  The data are shown as raw values (A) and means by group by study day (B) with the shaded areas representing 95% confident intervals of the means. The mean values (B) are also zoomed in to show the difference and trajectories two groups (C).

\newpage

```{r protein, echo=FALSE, warning=FALSE, fig.width=8,fig.height=8}
meandat <- aggregate(lft_protein ~ simple_Dx + study_day, dat, new_mean_ci)
meandat$mean <- meandat[,3][,1]
meandat$low <- meandat[,3][,2]
meandat$up <- meandat[,3][,3]

gA <- ggplot(dat, aes(dat, x = jstudy_day, col = simple_Dx, y = lft_protein))+
  geom_jitter(width = 0.07, shape = 1)+
  xlab("Study day")+
  ylab(TeX("Total protein (g/dL)"))+
  scale_color_manual(name = "Diagnosis", values = c("#EFC000FF","#0073C2FF"))+
  coord_cartesian(ylim = c(0,10))+
  theme(legend.position = "top")

gB <- ggplot(meandat,aes(x = study_day, col = simple_Dx))+
  geom_line(aes(y=mean,group=simple_Dx)) +
  geom_ribbon(aes(ymin = low,ymax=up,fill=simple_Dx), alpha = 0.3, col = NA)+
  xlab("Study day")+
  ylab(TeX("Total protein (g/dL)"))+
  scale_color_manual(name = "Diagnosis", values = c("#EFC000FF","#0073C2FF"))+
  scale_fill_manual(name = "Diagnosis", values = c("#EFC000FF","#0073C2FF"))+
  coord_cartesian(ylim = c(0,10))+
  theme(legend.position = "top")

gC <- ggplot(meandat,aes(x = study_day, col = simple_Dx))+
  geom_line(aes(y=mean,group=simple_Dx)) +
  geom_ribbon(aes(ymin = low,ymax=up,fill=simple_Dx), alpha = 0.3, col = NA)+
  xlab("Study day")+
  ylab(TeX("Total protein (g/dL)"))+
  scale_color_manual(name = "Diagnosis", values = c("#EFC000FF","#0073C2FF"))+
  scale_fill_manual(name = "Diagnosis", values = c("#EFC000FF","#0073C2FF"))+
  #coord_cartesian(ylim = c(0,10))+
  theme(legend.position = "top")

g <- ggarrange(gA,gB,gC,nrow = 2,ncol=2, labels = c("A","B","C"))
print(g)

ggsave(plot = g, filename = "../Plots/Supplement_protein.eps",width=8,height = 8,units = "in", device=cairo_ps)
```

**Fig. 11:** Time course of `Protein` (Total protein)  variable from study day one to five in two groups (DHF and Non-DHF).  The data are shown as raw values (A) and means by group by study day (B) with the shaded areas representing 95% confident intervals of the means. The mean values (B) are also zoomed in to show the difference and trajectories two groups (C).

\newpage

```{r albumin, echo=FALSE, warning=FALSE, fig.width=8,fig.height=8}
meandat <- aggregate(lft_albumin ~ simple_Dx + study_day, dat, new_mean_ci)
meandat$mean <- meandat[,3][,1]
meandat$low <- meandat[,3][,2]
meandat$up <- meandat[,3][,3]

gA <- ggplot(dat, aes(dat, x = jstudy_day, col = simple_Dx, y = lft_albumin))+
  geom_jitter(width = 0.07, shape = 1)+
  xlab("Study day")+
  ylab(TeX("Albumin (g/dL)"))+
  scale_color_manual(name = "Diagnosis", values = c("#EFC000FF","#0073C2FF"))+
  coord_cartesian(ylim = c(0,6))+
  theme(legend.position = "top")

gB <- ggplot(meandat,aes(x = study_day, col = simple_Dx))+
  geom_line(aes(y=mean,group=simple_Dx)) +
  geom_ribbon(aes(ymin = low,ymax=up,fill=simple_Dx), alpha = 0.3, col = NA)+
  xlab("Study day")+
  ylab(TeX("Albumin (g/dL)"))+
  scale_color_manual(name = "Diagnosis", values = c("#EFC000FF","#0073C2FF"))+
  scale_fill_manual(name = "Diagnosis", values = c("#EFC000FF","#0073C2FF"))+
  coord_cartesian(ylim = c(0,6))+
  theme(legend.position = "top")

gC <- ggplot(meandat,aes(x = study_day, col = simple_Dx))+
  geom_line(aes(y=mean,group=simple_Dx)) +
  geom_ribbon(aes(ymin = low,ymax=up,fill=simple_Dx), alpha = 0.3, col = NA)+
  xlab("Study day")+
  ylab(TeX("Albumin (g/dL)"))+
  scale_color_manual(name = "Diagnosis", values = c("#EFC000FF","#0073C2FF"))+
  scale_fill_manual(name = "Diagnosis", values = c("#EFC000FF","#0073C2FF"))+
  #coord_cartesian(ylim = c(0,6))+
  theme(legend.position = "top")

g <- ggarrange(gA,gB,gC,nrow = 2,ncol=2, labels = c("A","B","C"))
print(g)

ggsave(plot = g, filename = "../Plots/Supplement_Albumin.eps",width=8,height = 8,units = "in", device=cairo_ps)
```

**Fig. 12:** Time course of `Albumin`  variable from study day one to five in two groups (DHF and Non-DHF).  The data are shown as raw values (A) and means by group by study day (B) with the shaded areas representing 95% confident intervals of the means. The mean values (B) are also zoomed in to show the difference and trajectories two groups (C).

\newpage

```{r alt, echo=FALSE, warning=FALSE, fig.width=8,fig.height=8}
meandat <- aggregate(lft_alt ~ simple_Dx + study_day, dat, new_mean_ci)
meandat$mean <- meandat[,3][,1]
meandat$low <- meandat[,3][,2]
meandat$up <- meandat[,3][,3]

gA <- ggplot(dat, aes(dat, x = jstudy_day, col = simple_Dx, y = lft_alt))+
  geom_jitter(width = 0.07, shape = 1)+
  xlab("Study day")+
  ylab(TeX("ALT (IU/L)"))+
  scale_color_manual(name = "Diagnosis", values = c("#EFC000FF","#0073C2FF"))+
  coord_cartesian(ylim = c(0,3000))+
  theme(legend.position = "top")

gB <- ggplot(meandat,aes(x = study_day, col = simple_Dx))+
  geom_line(aes(y=mean,group=simple_Dx)) +
  geom_ribbon(aes(ymin = low,ymax=up,fill=simple_Dx), alpha = 0.3, col = NA)+
  xlab("Study day")+
  ylab(TeX("ALT (IU/L)"))+
  scale_color_manual(name = "Diagnosis", values = c("#EFC000FF","#0073C2FF"))+
  scale_fill_manual(name = "Diagnosis", values = c("#EFC000FF","#0073C2FF"))+
  coord_cartesian(ylim = c(0,3000))+
  theme(legend.position = "top")

gC <- ggplot(meandat,aes(x = study_day, col = simple_Dx))+
  geom_line(aes(y=mean,group=simple_Dx)) +
  geom_ribbon(aes(ymin = low,ymax=up,fill=simple_Dx), alpha = 0.3, col = NA)+
  xlab("Study day")+
  ylab(TeX("ALT (IU/L)"))+
  scale_color_manual(name = "Diagnosis", values = c("#EFC000FF","#0073C2FF"))+
  scale_fill_manual(name = "Diagnosis", values = c("#EFC000FF","#0073C2FF"))+
  #coord_cartesian(ylim = c(0,3000))+
  theme(legend.position = "top")

g <- ggarrange(gA,gB,gC,nrow = 2,ncol=2, labels = c("A","B","C"))
print(g)
ggsave(plot = g, filename = "../Plots/Supplement_ALT.eps",width=8,height = 8,units = "in", device=cairo_ps)
```

**Fig. 13:** Time course of `ALT` (Alanine transaminase)  variable from study day one to five in two groups (DHF and Non-DHF).  The data are shown as raw values (A) and means by group by study day (B) with the shaded areas representing 95% confident intervals of the means. The mean values (B) are also zoomed in to show the difference and trajectories two groups (C).

\newpage

```{r ast, echo=FALSE, warning=FALSE, fig.width=8,fig.height=8}
meandat <- aggregate(lft_ast ~ simple_Dx + study_day, dat, new_mean_ci)
meandat$mean <- meandat[,3][,1]
meandat$low <- meandat[,3][,2]
meandat$up <- meandat[,3][,3]

gA <- ggplot(dat, aes(dat, x = jstudy_day, col = simple_Dx, y = lft_ast))+
  geom_jitter(width = 0.07, shape = 1)+
  xlab("Study day")+
  ylab(TeX("AST (IU/L)"))+
  scale_color_manual(name = "Diagnosis", values = c("#EFC000FF","#0073C2FF"))+
  coord_cartesian(ylim = c(0,10000))+
  theme(legend.position = "top")

gB <- ggplot(meandat,aes(x = study_day, col = simple_Dx))+
  geom_line(aes(y=mean,group=simple_Dx)) +
  geom_ribbon(aes(ymin = low,ymax=up,fill=simple_Dx), alpha = 0.3, col = NA)+
  xlab("Study day")+
  ylab(TeX("AST (IU/L)"))+
  scale_color_manual(name = "Diagnosis", values = c("#EFC000FF","#0073C2FF"))+
  scale_fill_manual(name = "Diagnosis", values = c("#EFC000FF","#0073C2FF"))+
  coord_cartesian(ylim = c(0,10000))+
  theme(legend.position = "top")

gC <- ggplot(meandat,aes(x = study_day, col = simple_Dx))+
  geom_line(aes(y=mean,group=simple_Dx)) +
  geom_ribbon(aes(ymin = low,ymax=up,fill=simple_Dx), alpha = 0.3, col = NA)+
  xlab("Study day")+
  ylab(TeX("AST (IU/L)"))+
  scale_color_manual(name = "Diagnosis", values = c("#EFC000FF","#0073C2FF"))+
  scale_fill_manual(name = "Diagnosis", values = c("#EFC000FF","#0073C2FF"))+
  #coord_cartesian(ylim = c(0,10000))+
  theme(legend.position = "top")

g <- ggarrange(gA,gB,gC,nrow = 2,ncol=2, labels = c("A","B","C"))
print(g)

ggsave(plot = g, filename = "../Plots/Supplement_AST.eps",width=8,height = 8,units = "in", device=cairo_ps)
```

**Fig. 14:** Time course of `AST` (Aspartate transaminase)  variable from study day one to five in two groups (DHF and Non-DHF).  The data are shown as raw values (A) and means by group by study day (B) with the shaded areas representing 95% confident intervals of the means. The mean values (B) are also zoomed in to show the difference and trajectories two groups (C).

\newpage

```{r fluid, echo=FALSE, warning=FALSE, fig.width=8,fig.height=8}
meandat <- aggregate(fluid_ret ~ simple_Dx + study_day, dat, new_mean_ci)
meandat$mean <- meandat[,3][,1]
meandat$low <- meandat[,3][,2]
meandat$up <- meandat[,3][,3]

gA <- ggplot(dat, aes(dat, x = jstudy_day, col = simple_Dx, y = fluid_ret))+
  geom_jitter(width = 0.07, shape = 1)+
  xlab("Study day")+
  ylab(TeX("Fluid retention (ml)"))+
  scale_color_manual(name = "Diagnosis", values = c("#EFC000FF","#0073C2FF"))+
  coord_cartesian(ylim = c(-5000,5000))+
  theme(legend.position = "top")

gB <- ggplot(meandat,aes(x = study_day, col = simple_Dx))+
  geom_line(aes(y=mean,group=simple_Dx)) +
  geom_ribbon(aes(ymin = low,ymax=up,fill=simple_Dx), alpha = 0.3, col = NA)+
  xlab("Study day")+
   ylab(TeX("Fluid retention (ml)"))+
  scale_color_manual(name = "Diagnosis", values = c("#EFC000FF","#0073C2FF"))+
  scale_fill_manual(name = "Diagnosis", values = c("#EFC000FF","#0073C2FF"))+
  coord_cartesian(ylim = c(-5000,5000))+
  theme(legend.position = "top")

gC <- ggplot(meandat,aes(x = study_day, col = simple_Dx))+
  geom_line(aes(y=mean,group=simple_Dx)) +
  geom_ribbon(aes(ymin = low,ymax=up,fill=simple_Dx), alpha = 0.3, col = NA)+
  xlab("Study day")+
   ylab(TeX("Fluid retention (ml)"))+
  scale_color_manual(name = "Diagnosis", values = c("#EFC000FF","#0073C2FF"))+
  scale_fill_manual(name = "Diagnosis", values = c("#EFC000FF","#0073C2FF"))+
  #coord_cartesian(ylim = c(-5000,5000))+
  theme(legend.position = "top")

g <- ggarrange(gA,gB,gC,nrow = 2,ncol=2, labels = c("A","B","C"))
print(g)

ggsave(plot = g, filename = "../Plots/Supplement_fluid.eps",width=8,height = 8,units = "in", device=cairo_ps)
```

**Fig. 15:** Time course of `Fluid retention` variable from study day one to five in two groups (DHF and Non-DHF).  The data are shown as raw values (A) and means by group by study day (B) with the shaded areas representing 95% confident intervals of the means. The mean values (B) are also zoomed in to show the difference and trajectories two groups (C).

\newpage

```{r liver_size, echo=FALSE, warning=FALSE, fig.width=8,fig.height=8}
meandat <- aggregate(liver_size ~ simple_Dx + study_day, dat, new_mean_ci)
meandat$mean <- meandat[,3][,1]
meandat$low <- meandat[,3][,2]
meandat$up <- meandat[,3][,3]

gA <- ggplot(dat, aes(dat, x = jstudy_day, col = simple_Dx, y = liver_size))+
  geom_jitter(width = 0.07, shape = 1)+
  xlab("Study day")+
  ylab(TeX("Liver size (cm)"))+
  scale_color_manual(name = "Diagnosis", values = c("#EFC000FF","#0073C2FF"))+
  coord_cartesian(ylim = c(0,8))+
  theme(legend.position = "top")

gB <- ggplot(meandat,aes(x = study_day, col = simple_Dx))+
  geom_line(aes(y=mean,group=simple_Dx)) +
  geom_ribbon(aes(ymin = low,ymax=up,fill=simple_Dx), alpha = 0.3, col = NA)+
  xlab("Study day")+
  ylab(TeX("Liver size (cm)"))+
  scale_color_manual(name = "Diagnosis", values = c("#EFC000FF","#0073C2FF"))+
  scale_fill_manual(name = "Diagnosis", values = c("#EFC000FF","#0073C2FF"))+
  coord_cartesian(ylim = c(0,8))+
  theme(legend.position = "top")

gC <- ggplot(meandat,aes(x = study_day, col = simple_Dx))+
  geom_line(aes(y=mean,group=simple_Dx)) +
  geom_ribbon(aes(ymin = low,ymax=up,fill=simple_Dx), alpha = 0.3, col = NA)+
  xlab("Study day")+
  ylab(TeX("Liver size (cm)"))+
  scale_color_manual(name = "Diagnosis", values = c("#EFC000FF","#0073C2FF"))+
  scale_fill_manual(name = "Diagnosis", values = c("#EFC000FF","#0073C2FF"))+
  #coord_cartesian(ylim = c(0,8))+
  theme(legend.position = "top")

g <- ggarrange(gA,gB,gC,nrow = 2,ncol=2, labels = c("A","B","C"))
print(g)
ggsave(plot = g, filename = "../Plots/Supplement_liver_size.eps",width=8,height = 8,units = "in", device=cairo_ps)
```

**Fig. 16:** Time course of `Liver size` variable from study day one to five in two groups (DHF and Non-DHF).  The data are shown as raw values (A) and means by group by study day (B) with the shaded areas representing 95% confident intervals of the means. The mean values (B) are also zoomed in to show the difference and trajectories two groups (C).

\newpage

```{r ab_circum, echo=FALSE, warning=FALSE, fig.width=8,fig.height=8}
meandat <- aggregate(ab_circum ~ simple_Dx + study_day, dat, new_mean_ci)
meandat$mean <- meandat[,3][,1]
meandat$low <- meandat[,3][,2]
meandat$up <- meandat[,3][,3]

gA <- ggplot(dat, aes(dat, x = jstudy_day, col = simple_Dx, y = ab_circum))+
  geom_jitter(width = 0.07, shape = 1)+
  xlab("Study day")+
  ylab(TeX("Abdominal circumference (cm)"))+
  scale_color_manual(name = "Diagnosis", values = c("#EFC000FF","#0073C2FF"))+
  coord_cartesian(ylim = c(0,110))+
  theme(legend.position = "top")

gB <- ggplot(meandat,aes(x = study_day, col = simple_Dx))+
  geom_line(aes(y=mean,group=simple_Dx)) +
  geom_ribbon(aes(ymin = low,ymax=up,fill=simple_Dx), alpha = 0.3, col = NA)+
  xlab("Study day")+
  ylab(TeX("Abdominal circumference (cm)"))+
  scale_color_manual(name = "Diagnosis", values = c("#EFC000FF","#0073C2FF"))+
  scale_fill_manual(name = "Diagnosis", values = c("#EFC000FF","#0073C2FF"))+
  coord_cartesian(ylim = c(0,110))+
  theme(legend.position = "top")

gC <- ggplot(meandat,aes(x = study_day, col = simple_Dx))+
  geom_line(aes(y=mean,group=simple_Dx)) +
  geom_ribbon(aes(ymin = low,ymax=up,fill=simple_Dx), alpha = 0.3, col = NA)+
  xlab("Study day")+
  ylab(TeX("Abdominal circumference (cm)"))+
  scale_color_manual(name = "Diagnosis", values = c("#EFC000FF","#0073C2FF"))+
  scale_fill_manual(name = "Diagnosis", values = c("#EFC000FF","#0073C2FF"))+
  #coord_cartesian(ylim = c(0,110))+
  theme(legend.position = "top")

g <- ggarrange(gA,gB,gC,nrow = 2,ncol=2, labels = c("A","B","C"))
print(g)
ggsave(plot = g, filename = "../Plots/Supplement_ab_cir.eps",width=8,height = 8,units = "in", device=cairo_ps)
```

**Fig. 17:** Time course of `Abdominal circumference` variable from study day one to five in two groups (DHF and Non-DHF).  The data are shown as raw values (A) and means by group by study day (B) with the shaded areas representing 95% confident intervals of the means. The mean values (B) are also zoomed in to show the difference and trajectories two groups (C).

\newpage

```{r weight, echo=FALSE, warning=FALSE, fig.width=8,fig.height=8}
meandat <- aggregate(weight ~ simple_Dx + study_day, dat, new_mean_ci)
meandat$mean <- meandat[,3][,1]
meandat$low <- meandat[,3][,2]
meandat$up <- meandat[,3][,3]

gA <- ggplot(dat, aes(dat, x = jstudy_day, col = simple_Dx, y = weight))+
  geom_jitter(width = 0.07, shape = 1)+
  xlab("Study day")+
  ylab(TeX("Weight (kg)"))+
  scale_color_manual(name = "Diagnosis", values = c("#EFC000FF","#0073C2FF"))+
  coord_cartesian(ylim = c(0,105))+
  theme(legend.position = "top")

gB <- ggplot(meandat,aes(x = study_day, col = simple_Dx))+
  geom_line(aes(y=mean,group=simple_Dx)) +
  geom_ribbon(aes(ymin = low,ymax=up,fill=simple_Dx), alpha = 0.3, col = NA)+
  xlab("Study day")+
  ylab(TeX("Weight (kg)"))+
  scale_color_manual(name = "Diagnosis", values = c("#EFC000FF","#0073C2FF"))+
  scale_fill_manual(name = "Diagnosis", values = c("#EFC000FF","#0073C2FF"))+
  coord_cartesian(ylim = c(0,105))+
  theme(legend.position = "top")

gC <- ggplot(meandat,aes(x = study_day, col = simple_Dx))+
  geom_line(aes(y=mean,group=simple_Dx)) +
  geom_ribbon(aes(ymin = low,ymax=up,fill=simple_Dx), alpha = 0.3, col = NA)+
  xlab("Study day")+
  ylab(TeX("Weight (kg)"))+
  scale_color_manual(name = "Diagnosis", values = c("#EFC000FF","#0073C2FF"))+
  scale_fill_manual(name = "Diagnosis", values = c("#EFC000FF","#0073C2FF"))+
  #coord_cartesian(ylim = c(0,105))+
  theme(legend.position = "top")

g <- ggarrange(gA,gB,gC,nrow = 2,ncol=2, labels = c("A","B","C"))
print(g)
ggsave(plot = g, filename = "../Plots/Supplement_weight.eps",width=8,height = 8,units = "in", device=cairo_ps)
```

**Fig. 18:** Time course of `Weight` variable from study day one to five in two groups (DHF and Non-DHF).  The data are shown as raw values (A) and means by group by study day (B) with the shaded areas representing 95% confident intervals of the means. The mean values (B) are also zoomed in to show the difference and trajectories two groups (C).

\newpage

```{r temp_max, echo=FALSE, warning=FALSE, fig.width=8,fig.height=8}
meandat <- aggregate(temp_max ~ simple_Dx + study_day, dat, new_mean_ci)
meandat$mean <- meandat[,3][,1]
meandat$low <- meandat[,3][,2]
meandat$up <- meandat[,3][,3]

gA <- ggplot(dat, aes(dat, x = jstudy_day, col = simple_Dx, y = temp_max))+
  geom_jitter(width = 0.07, shape = 1)+
  xlab("Study day")+
  ylab(TeX("Maximum temperature (celcius)"))+
  scale_color_manual(name = "Diagnosis", values = c("#EFC000FF","#0073C2FF"))+
  coord_cartesian(ylim = c(35,43))+
  theme(legend.position = "top")

gB <- ggplot(meandat,aes(x = study_day, col = simple_Dx))+
  geom_line(aes(y=mean,group=simple_Dx)) +
  geom_ribbon(aes(ymin = low,ymax=up,fill=simple_Dx), alpha = 0.3, col = NA)+
  xlab("Study day")+
  ylab(TeX("Maximum temperature (celcius)"))+
  scale_color_manual(name = "Diagnosis", values = c("#EFC000FF","#0073C2FF"))+
  scale_fill_manual(name = "Diagnosis", values = c("#EFC000FF","#0073C2FF"))+
  coord_cartesian(ylim = c(35,43))+
  theme(legend.position = "top")

gC <- ggplot(meandat,aes(x = study_day, col = simple_Dx))+
  geom_line(aes(y=mean,group=simple_Dx)) +
  geom_ribbon(aes(ymin = low,ymax=up,fill=simple_Dx), alpha = 0.3, col = NA)+
  xlab("Study day")+
  ylab(TeX("Maximum temperature (celcius)"))+
  scale_color_manual(name = "Diagnosis", values = c("#EFC000FF","#0073C2FF"))+
  scale_fill_manual(name = "Diagnosis", values = c("#EFC000FF","#0073C2FF"))+
  #coord_cartesian(ylim = c(35,43))+
  theme(legend.position = "top")

g <- ggarrange(gA,gB,gC,nrow = 2,ncol=2, labels = c("A","B","C"))
print(g)
ggsave(plot = g, filename = "../Plots/Supplement_max_temp.eps",width=8,height = 8,units = "in", device=cairo_ps)

```

**Fig. 19:** Time course of `Maximum temperature` variable from study day one to five in two groups (DHF and Non-DHF).  The data are shown as raw values (A) and means by group by study day (B) with the shaded areas representing 95% confident intervals of the means. The mean values (B) are also zoomed in to show the difference and trajectories two groups (C).

\newpage

```{r temp_min, echo=FALSE, warning=FALSE, fig.width=8,fig.height=8}
meandat <- aggregate(temp_min ~ simple_Dx + study_day, dat, new_mean_ci)
meandat$mean <- meandat[,3][,1]
meandat$low <- meandat[,3][,2]
meandat$up <- meandat[,3][,3]

gA <- ggplot(dat, aes(dat, x = jstudy_day, col = simple_Dx, y = temp_min))+
  geom_jitter(width = 0.07, shape = 1)+
  xlab("Study day")+
  ylab(TeX("Minimum temperature (celcius)"))+
  scale_color_manual(name = "Diagnosis", values = c("#EFC000FF","#0073C2FF"))+
  coord_cartesian(ylim = c(35,43))+
  theme(legend.position = "top")

gB <- ggplot(meandat,aes(x = study_day, col = simple_Dx))+
  geom_line(aes(y=mean,group=simple_Dx)) +
  geom_ribbon(aes(ymin = low,ymax=up,fill=simple_Dx), alpha = 0.3, col = NA)+
  xlab("Study day")+
  ylab(TeX("Minimum temperature (celcius)"))+
  scale_color_manual(name = "Diagnosis", values = c("#EFC000FF","#0073C2FF"))+
  scale_fill_manual(name = "Diagnosis", values = c("#EFC000FF","#0073C2FF"))+
  coord_cartesian(ylim = c(35,43))+
  theme(legend.position = "top")

gC <- ggplot(meandat,aes(x = study_day, col = simple_Dx))+
  geom_line(aes(y=mean,group=simple_Dx)) +
  geom_ribbon(aes(ymin = low,ymax=up,fill=simple_Dx), alpha = 0.3, col = NA)+
  xlab("Study day")+
  ylab(TeX("Minimum temperature (celcius)"))+
  scale_color_manual(name = "Diagnosis", values = c("#EFC000FF","#0073C2FF"))+
  scale_fill_manual(name = "Diagnosis", values = c("#EFC000FF","#0073C2FF"))+
  #coord_cartesian(ylim = c(35,43))+
  theme(legend.position = "top")

g <- ggarrange(gA,gB,gC,nrow = 2,ncol=2, labels = c("A","B","C"))
print(g)

ggsave(plot = g, filename = "../Plots/Supplement_min_temp.eps",width=8,height = 8,units = "in", device=cairo_ps)
```

**Fig. 20:** Time course of `Minimum temperature` variable from study day one to five in two groups (DHF and Non-DHF).  The data are shown as raw values (A) and means by group by study day (B) with the shaded areas representing 95% confident intervals of the means. The mean values (B) are also zoomed in to show the difference and trajectories two groups (C).

\newpage

```{r sbp, echo=FALSE, warning=FALSE, fig.width=8,fig.height=8}
meandat <- aggregate(sbp ~ simple_Dx + study_day, dat, new_mean_ci)
meandat$mean <- meandat[,3][,1]
meandat$low <- meandat[,3][,2]
meandat$up <- meandat[,3][,3]

gA <- ggplot(dat, aes(dat, x = jstudy_day, col = simple_Dx, y = sbp))+
  geom_jitter(width = 0.07, shape = 1)+
  xlab("Study day")+
  ylab(TeX("SBP (mmHg)"))+
  scale_color_manual(name = "Diagnosis", values = c("#EFC000FF","#0073C2FF"))+
  coord_cartesian(ylim = c(60,140))+
  theme(legend.position = "top")

gB <- ggplot(meandat,aes(x = study_day, col = simple_Dx))+
  geom_line(aes(y=mean,group=simple_Dx)) +
  geom_ribbon(aes(ymin = low,ymax=up,fill=simple_Dx), alpha = 0.3, col = NA)+
  xlab("Study day")+
  ylab(TeX("SBP (mmHg)"))+
  scale_color_manual(name = "Diagnosis", values = c("#EFC000FF","#0073C2FF"))+
  scale_fill_manual(name = "Diagnosis", values = c("#EFC000FF","#0073C2FF"))+
  coord_cartesian(ylim = c(60,140))+
  theme(legend.position = "top")

gC <- ggplot(meandat,aes(x = study_day, col = simple_Dx))+
  geom_line(aes(y=mean,group=simple_Dx)) +
  geom_ribbon(aes(ymin = low,ymax=up,fill=simple_Dx), alpha = 0.3, col = NA)+
  xlab("Study day")+
  ylab(TeX("SBP (mmHg)"))+
  scale_color_manual(name = "Diagnosis", values = c("#EFC000FF","#0073C2FF"))+
  scale_fill_manual(name = "Diagnosis", values = c("#EFC000FF","#0073C2FF"))+
  #coord_cartesian(ylim = c(60,140))+
  theme(legend.position = "top")

g <- ggarrange(gA,gB,gC,nrow = 2,ncol=2, labels = c("A","B","C"))
print(g)

ggsave(plot = g, filename = "../Plots/Supplement_sbp.eps",width=8,height = 8,units = "in", device=cairo_ps)
```

**Fig. 21:** Time course of `SBP` (Systolic blood pressure) variable from study day one to five in two groups (DHF and Non-DHF).  The data are shown as raw values (A) and means by group by study day (B) with the shaded areas representing 95% confident intervals of the means. The mean values (B) are also zoomed in to show the difference and trajectories two groups (C).

\newpage

```{r dbp, echo=FALSE, warning=FALSE, fig.width=8,fig.height=8}
meandat <- aggregate(dbp ~ simple_Dx + study_day, dat, new_mean_ci)
meandat$mean <- meandat[,3][,1]
meandat$low <- meandat[,3][,2]
meandat$up <- meandat[,3][,3]

gA <- ggplot(dat, aes(dat, x = jstudy_day, col = simple_Dx, y = dbp))+
  geom_jitter(width = 0.07, shape = 1)+
  xlab("Study day")+
  ylab(TeX("DBP (mmHg)"))+
  scale_color_manual(name = "Diagnosis", values = c("#EFC000FF","#0073C2FF"))+
  coord_cartesian(ylim = c(30,100))+
  theme(legend.position = "top")

gB <- ggplot(meandat,aes(x = study_day, col = simple_Dx))+
  geom_line(aes(y=mean,group=simple_Dx)) +
  geom_ribbon(aes(ymin = low,ymax=up,fill=simple_Dx), alpha = 0.3, col = NA)+
  xlab("Study day")+
  ylab(TeX("DBP (mmHg)"))+
  scale_color_manual(name = "Diagnosis", values = c("#EFC000FF","#0073C2FF"))+
  scale_fill_manual(name = "Diagnosis", values = c("#EFC000FF","#0073C2FF"))+
  coord_cartesian(ylim = c(30,100))+
  theme(legend.position = "top")

gC <- ggplot(meandat,aes(x = study_day, col = simple_Dx))+
  geom_line(aes(y=mean,group=simple_Dx)) +
  geom_ribbon(aes(ymin = low,ymax=up,fill=simple_Dx), alpha = 0.3, col = NA)+
  xlab("Study day")+
  ylab(TeX("DBP (mmHg)"))+
  scale_color_manual(name = "Diagnosis", values = c("#EFC000FF","#0073C2FF"))+
  scale_fill_manual(name = "Diagnosis", values = c("#EFC000FF","#0073C2FF"))+
  #coord_cartesian(ylim = c(30,100))+
  theme(legend.position = "top")

g <- ggarrange(gA,gB,gC,nrow = 2,ncol=2, labels = c("A","B","C"))
print(g)
ggsave(plot = g, filename = "../Plots/Supplement_dbp.eps",width=8,height = 8,units = "in", device=cairo_ps)
```

**Fig. 22:** Time course of `DBP` (Diastolic blood pressure) variable from study day one to five in two groups (DHF and Non-DHF).  The data are shown as raw values (A) and means by group by study day (B) with the shaded areas representing 95% confident intervals of the means. The mean values (B) are also zoomed in to show the difference and trajectories two groups (C).

\newpage

```{r pulse_pre_min, echo=FALSE, warning=FALSE, fig.width=8,fig.height=8}
meandat <- aggregate(pulse_pre_min ~ simple_Dx + study_day, dat, new_mean_ci)
meandat$mean <- meandat[,3][,1]
meandat$low <- meandat[,3][,2]
meandat$up <- meandat[,3][,3]

gA <- ggplot(dat, aes(dat, x = jstudy_day, col = simple_Dx, y = pulse_pre_min))+
  geom_jitter(width = 0.07, shape = 1)+
  xlab("Study day")+
  ylab(TeX("Minimum pulse pressure (mmHg)"))+
  scale_color_manual(name = "Diagnosis", values = c("#EFC000FF","#0073C2FF"))+
  coord_cartesian(ylim = c(0,61))+
  theme(legend.position = "top")

gB <- ggplot(meandat,aes(x = study_day, col = simple_Dx))+
  geom_line(aes(y=mean,group=simple_Dx)) +
  geom_ribbon(aes(ymin = low,ymax=up,fill=simple_Dx), alpha = 0.3, col = NA)+
  xlab("Study day")+
   ylab(TeX("Minimum pulse pressure (mmHg)"))+
  scale_color_manual(name = "Diagnosis", values = c("#EFC000FF","#0073C2FF"))+
  scale_fill_manual(name = "Diagnosis", values = c("#EFC000FF","#0073C2FF"))+
  coord_cartesian(ylim = c(0,61))+
  theme(legend.position = "top")

gC <- ggplot(meandat,aes(x = study_day, col = simple_Dx))+
  geom_line(aes(y=mean,group=simple_Dx)) +
  geom_ribbon(aes(ymin = low,ymax=up,fill=simple_Dx), alpha = 0.3, col = NA)+
  xlab("Study day")+
   ylab(TeX("Minimum pulse pressure (mmHg)"))+
  scale_color_manual(name = "Diagnosis", values = c("#EFC000FF","#0073C2FF"))+
  scale_fill_manual(name = "Diagnosis", values = c("#EFC000FF","#0073C2FF"))+
  #coord_cartesian(ylim = c(0,61))+
  theme(legend.position = "top")

g <- ggarrange(gA,gB,gC,nrow = 2,ncol=2, labels = c("A","B","C"))
print(g)

ggsave(plot = g, filename = "../Plots/Supplement_pulse_press.eps",width=8,height = 8,units = "in", device=cairo_ps)
```

**Fig. 23:** Time course of `Minimum pulse pressure`  variable from study day one to five in two groups (DHF and Non-DHF).  The data are shown as raw values (A) and means by group by study day (B) with the shaded areas representing 95% confident intervals of the means. The mean values (B) are also zoomed in to show the difference and trajectories two groups (C).

\newpage

```{r pulse_rate_max, echo=FALSE, warning=FALSE, fig.width=8,fig.height=8}
meandat <- aggregate(pulse_rate_max ~ simple_Dx + study_day, dat, new_mean_ci)
meandat$mean <- meandat[,3][,1]
meandat$low <- meandat[,3][,2]
meandat$up <- meandat[,3][,3]

gA <- ggplot(dat, aes(dat, x = jstudy_day, col = simple_Dx, y = pulse_rate_max))+
  geom_jitter(width = 0.07, shape = 1)+
  xlab("Study day")+
  ylab(TeX("Maximum pulse rate (beat/minute)"))+
  scale_color_manual(name = "Diagnosis", values = c("#EFC000FF","#0073C2FF"))+
  coord_cartesian(ylim = c(60,180))+
  theme(legend.position = "top")

gB <- ggplot(meandat,aes(x = study_day, col = simple_Dx))+
  geom_line(aes(y=mean,group=simple_Dx)) +
  geom_ribbon(aes(ymin = low,ymax=up,fill=simple_Dx), alpha = 0.3, col = NA)+
  xlab("Study day")+
  ylab(TeX("Maximum pulse rate (beat/minute)"))+
  scale_color_manual(name = "Diagnosis", values = c("#EFC000FF","#0073C2FF"))+
  scale_fill_manual(name = "Diagnosis", values = c("#EFC000FF","#0073C2FF"))+
  coord_cartesian(ylim = c(60,180))+
  theme(legend.position = "top")

gC <- ggplot(meandat,aes(x = study_day, col = simple_Dx))+
  geom_line(aes(y=mean,group=simple_Dx)) +
  geom_ribbon(aes(ymin = low,ymax=up,fill=simple_Dx), alpha = 0.3, col = NA)+
  xlab("Study day")+
  ylab(TeX("Maximum pulse rate (beat/minute)"))+
  scale_color_manual(name = "Diagnosis", values = c("#EFC000FF","#0073C2FF"))+
  scale_fill_manual(name = "Diagnosis", values = c("#EFC000FF","#0073C2FF"))+
  #coord_cartesian(ylim = c(60,180))+
  theme(legend.position = "top")

g <- ggarrange(gA,gB,gC,nrow = 2,ncol=2, labels = c("A","B","C"))
print(g)
ggsave(plot = g, filename = "../Plots/Supplement_max_pulse.eps",width=8,height = 8,units = "in", device=cairo_ps)
```

**Fig. 24:** Time course of `Maximum pulse rate`  variable from study day one to five in two groups (DHF and Non-DHF).  The data are shown as raw values (A) and means by group by study day (B) with the shaded areas representing 95% confident intervals of the means. The mean values (B) are also zoomed in to show the difference and trajectories two groups (C).

\newpage

```{r pulse_rate_min, echo=FALSE, warning=FALSE, fig.width=8,fig.height=8}
meandat <- aggregate(pulse_rate_min ~ simple_Dx + study_day, dat, new_mean_ci)
meandat$mean <- meandat[,3][,1]
meandat$low <- meandat[,3][,2]
meandat$up <- meandat[,3][,3]

gA <- ggplot(dat, aes(dat, x = jstudy_day, col = simple_Dx, y = pulse_rate_min))+
  geom_jitter(width = 0.07, shape = 1)+
  xlab("Study day")+
  ylab(TeX("Minimum pulse rate (beat/minute)"))+
  scale_color_manual(name = "Diagnosis", values = c("#EFC000FF","#0073C2FF"))+
  coord_cartesian(ylim = c(40,140))+
  theme(legend.position = "top")

gB <- ggplot(meandat,aes(x = study_day, col = simple_Dx))+
  geom_line(aes(y=mean,group=simple_Dx)) +
  geom_ribbon(aes(ymin = low,ymax=up,fill=simple_Dx), alpha = 0.3, col = NA)+
  xlab("Study day")+
  ylab(TeX("Minimum pulse rate (beat/minute)"))+
  scale_color_manual(name = "Diagnosis", values = c("#EFC000FF","#0073C2FF"))+
  scale_fill_manual(name = "Diagnosis", values = c("#EFC000FF","#0073C2FF"))+
  coord_cartesian(ylim = c(40,140))+
  theme(legend.position = "top")

gC <- ggplot(meandat,aes(x = study_day, col = simple_Dx))+
  geom_line(aes(y=mean,group=simple_Dx)) +
  geom_ribbon(aes(ymin = low,ymax=up,fill=simple_Dx), alpha = 0.3, col = NA)+
  xlab("Study day")+
  ylab(TeX("Minimum pulse rate (beat/minute)"))+
  scale_color_manual(name = "Diagnosis", values = c("#EFC000FF","#0073C2FF"))+
  scale_fill_manual(name = "Diagnosis", values = c("#EFC000FF","#0073C2FF"))+
  #coord_cartesian(ylim = c(40,140))+
  theme(legend.position = "top")

g <- ggarrange(gA,gB,gC,nrow = 2,ncol=2, labels = c("A","B","C"))
print(g)
ggsave(plot = g, filename = "../Plots/Supplement_min_pulse.eps",width=8,height = 8,units = "in", device=cairo_ps)
```

**Fig. 25:** Time course of `Minimum pulse rate`  variable from study day one to five in two groups (DHF and Non-DHF).  The data are shown as raw values (A) and means by group by study day (B) with the shaded areas representing 95% confident intervals of the means. The mean values (B) are also zoomed in to show the difference and trajectories two groups (C).

\newpage

```{r hct_max, echo=FALSE, warning=FALSE, fig.width=8,fig.height=8}
meandat <- aggregate(hct_max ~ simple_Dx + study_day, dat, new_mean_ci)
meandat$mean <- meandat[,3][,1]
meandat$low <- meandat[,3][,2]
meandat$up <- meandat[,3][,3]

gA <- ggplot(dat, aes(dat, x = jstudy_day, col = simple_Dx, y = hct_max))+
  geom_jitter(width = 0.07, shape = 1)+
  xlab("Study day")+
  ylab(TeX("Maximum fingertip hematocrit (%)"))+
  scale_color_manual(name = "Diagnosis", values = c("#EFC000FF","#0073C2FF"))+
  coord_cartesian(ylim = c(20,70))+
  theme(legend.position = "top")

gB <- ggplot(meandat,aes(x = study_day, col = simple_Dx))+
  geom_line(aes(y=mean,group=simple_Dx)) +
  geom_ribbon(aes(ymin = low,ymax=up,fill=simple_Dx), alpha = 0.3, col = NA)+
  xlab("Study day")+
  ylab(TeX("Maximum fingertip hematocrit (%)"))+
  scale_color_manual(name = "Diagnosis", values = c("#EFC000FF","#0073C2FF"))+
  scale_fill_manual(name = "Diagnosis", values = c("#EFC000FF","#0073C2FF"))+
  coord_cartesian(ylim = c(20,70))+
  theme(legend.position = "top")

gC <- ggplot(meandat,aes(x = study_day, col = simple_Dx))+
  geom_line(aes(y=mean,group=simple_Dx)) +
  geom_ribbon(aes(ymin = low,ymax=up,fill=simple_Dx), alpha = 0.3, col = NA)+
  xlab("Study day")+
  ylab(TeX("Maximum fingertip hematocrit (%)"))+
  scale_color_manual(name = "Diagnosis", values = c("#EFC000FF","#0073C2FF"))+
  scale_fill_manual(name = "Diagnosis", values = c("#EFC000FF","#0073C2FF"))+
  #coord_cartesian(ylim = c(20,70))+
  theme(legend.position = "top")

g <- ggarrange(gA,gB,gC,nrow = 2,ncol=2, labels = c("A","B","C"))
print(g)

ggsave(plot = g, filename = "../Plots/Supplement_max_hct_ward.eps",width=8,height = 8,units = "in", device=cairo_ps)
```

**Fig. 26:** Time course of `Maximum fingertip hematocrit`  variable from study day one to five in two groups (DHF and Non-DHF).  The data are shown as raw values (A) and means by group by study day (B) with the shaded areas representing 95% confident intervals of the means. The mean values (B) are also zoomed in to show the difference and trajectories two groups (C).

\newpage

```{r hct_min, echo=FALSE, warning=FALSE, fig.width=8,fig.height=8}
meandat <- aggregate(hct_min ~ simple_Dx + study_day, dat, new_mean_ci)
meandat$mean <- meandat[,3][,1]
meandat$low <- meandat[,3][,2]
meandat$up <- meandat[,3][,3]

gA <- ggplot(dat, aes(dat, x = jstudy_day, col = simple_Dx, y = hct_min))+
  geom_jitter(width = 0.07, shape = 1)+
  xlab("Study day")+
  ylab(TeX("Minimum fingertip hematocrit (%)"))+
  scale_color_manual(name = "Diagnosis", values = c("#EFC000FF","#0073C2FF"))+
  coord_cartesian(ylim = c(0,60))+
  theme(legend.position = "top")

gB <- ggplot(meandat,aes(x = study_day, col = simple_Dx))+
  geom_line(aes(y=mean,group=simple_Dx)) +
  geom_ribbon(aes(ymin = low,ymax=up,fill=simple_Dx), alpha = 0.3, col = NA)+
  xlab("Study day")+
  ylab(TeX("Minimum fingertip hematocrit (%)"))+
  scale_color_manual(name = "Diagnosis", values = c("#EFC000FF","#0073C2FF"))+
  scale_fill_manual(name = "Diagnosis", values = c("#EFC000FF","#0073C2FF"))+
  coord_cartesian(ylim = c(0,60))+
  theme(legend.position = "top")

gC <- ggplot(meandat,aes(x = study_day, col = simple_Dx))+
  geom_line(aes(y=mean,group=simple_Dx)) +
  geom_ribbon(aes(ymin = low,ymax=up,fill=simple_Dx), alpha = 0.3, col = NA)+
  xlab("Study day")+
  ylab(TeX("Minimum fingertip hematocrit (%)"))+
  scale_color_manual(name = "Diagnosis", values = c("#EFC000FF","#0073C2FF"))+
  scale_fill_manual(name = "Diagnosis", values = c("#EFC000FF","#0073C2FF"))+
  #coord_cartesian(ylim = c(0,60))+
  theme(legend.position = "top")

g <- ggarrange(gA,gB,gC,nrow = 2,ncol=2, labels = c("A","B","C"))
print(g)
ggsave(plot = g, filename = "../Plots/Supplement_min_hct_ward.eps",width=8,height = 8,units = "in", device=cairo_ps)
```

**Fig. 27:** Time course of `Minimum fingertip hematocrit`  variable from study day one to five in two groups (DHF and Non-DHF).  The data are shown as raw values (A) and means by group by study day (B) with the shaded areas representing 95% confident intervals of the means. The mean values (B) are also zoomed in to show the difference and trajectories two groups (C).