---
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readr)
library(lubridate)
library(tidyverse)
library(stringr)
library(ggpubr)
library(rstatix)

dat <- read_csv("~/R/R_Projects/DengueAI/RawData/_DATA_2022-12-01_1125.csv")
dat1 <- read_csv("~/R/R_Projects/DengueAI/RawData/_DATA_LABELS_2022-12-01_1122.csv")
dat2 <- read_csv("~/R/R_Projects/DengueAI/RawData/CoDEN_for_Peter_20201002.csv")

theme_set(theme_bw())

#### mean_ci function
new_mean_ci <- function(vector, alpha = 0.05, na.rm = T){
  if(na.rm){
  n_vector <- vector[!is.na(vector)]
  }else{
    n_vector <- vector
  }
  
  sample.mean <- mean(n_vector)
  sample.n <- length(n_vector)
  sample.sd <- sd(n_vector)
  sample.se <- sample.sd/sqrt(sample.n)
  
  degrees.freedom = sample.n - 1
  t.score = qt(p=alpha/2, df=degrees.freedom,lower.tail=F)
  
  margin.error <- t.score * sample.se
  lower.bound <- sample.mean - margin.error
  upper.bound <- sample.mean + margin.error
  
  return(cbind(c(sample.mean,lower.bound,upper.bound)))
}

# Format Dx and Day0
DX_Day0 <- dat1[!is.na(dat1$`Final Dx`),c("SNO:","Final Dx","Final D0")]
DX_Day0$simple_Dx <- "DHF"
DX_Day0$simple_Dx[which(DX_Day0$`Final Dx` == "Not dengue")] <- "OFI"
DX_Day0$simple_Dx[which(DX_Day0$`Final Dx` == "DF")] <- "DF"
DX_Day0$final_day0 <- ymd(DX_Day0$`Final D0`)
DX_Day0$`Final Dx` <- DX_Day0$`Final D0` <- NULL

dat <- merge(dat,DX_Day0, by.x = "sno",by.y="SNO:")

# Format Site
dat$site <- factor((substr(dat$sno,3,3)),levels = 1:2, labels = c("KK","SK"))

# Format to_day0
dat$date <- ymd(dat$date_d04)
dat$to_day0 <- dat$date - dat$final_day0

# Format study day
dat$study_day <- as.numeric(str_match(dat$redcap_event_name, ".?study_day_([0-9])_arm_1")[,2])

# Format fever day
fever <- dat[!is.na(dat$fever_date), c("sno","fever_date")]
fever$f_date <- ymd(fever$fever_date)
dat <- merge(dat,fever, by = "sno", all.x = T)
dat$fever_day <- dat$date - dat$f_date

dat <- dat[which(dat$simple_Dx != "OFI"),]
dat$simple_Dx <- factor(dat$simple_Dx, levels = c("DHF","DF"), labels = c("DHF","Non-DHF"))


#### Use identical dataset as Peter's ####
dat <- dat[dat$sno %in% unique(dat2$d01_sno),]
#### Show <= 5 study day
dat <- dat[which(dat$study_day <= 5),]
### Jitter study day
dat$jstudy_day <- dat$study_day + 0.1
dat$jstudy_day[dat$simple_Dx == "Non-DHF"] <- dat$study_day[dat$simple_Dx == "Non-DHF"] - 0.1



dat$study_day <- factor(dat$study_day, levels = 1:5, labels = paste0("Study Day",1:5))
dat$simple_Dx <- factor(dat$simple_Dx, levels = c("Non-DHF","DHF")) 
```


```{r bleeding, echo=FALSE, warning=FALSE, fig.width=10,fig.height=5}
dat$bleeding_d04_f <- NA
dat$bleeding_d04_f[which(dat$bleeding_d04 == 2)] <- "Yes"
dat$bleeding_d04_f[which(dat$bleeding_d04 == 1)] <- "No"


cdat <- aggregate(sno ~ simple_Dx +study_day + bleeding_d04_f, dat[!is.na(dat$bleeding_d04_f),],FUN = length)

pdat <- aggregate(sno ~ simple_Dx +study_day , dat[!is.na(dat$bleeding_d04_f),],FUN = length)
pdat <- merge(cdat,pdat, by = c("simple_Dx","study_day"))
pdat$perc <- 100*(pdat$sno.x/pdat$sno.y)

gA <- ggplot(cdat,aes(x=simple_Dx,fill = bleeding_d04_f,  y = sno))+
  geom_bar(stat="identity", lwd = 1)+
  scale_fill_manual(name = "Bleeding", values = c("gray","gray5"))+
  xlab("")+
  ylab("Number of patients")+
  facet_grid(.~study_day)+
  theme(legend.position = "top",
        axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))

gB <-ggplot(pdat,aes(x=simple_Dx,fill = bleeding_d04_f,  y = perc))+
  geom_bar(stat="identity", lwd = 1)+
  scale_fill_manual(name = "Bleeding", values = c("gray","gray5"))+
  xlab("")+
  ylab("Proportion of patients (%)")+
  facet_grid(.~study_day)+
  theme(legend.position = "top",
        axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))

g <- ggarrange(gA,gB,ncol = 2,nrow = 1, labels = c("A","B"))
print(g)
ggsave(plot = g, filename = "../Plots/Supplement_bleeding.eps",width=10,height = 5,units = "in", device=cairo_ps)
```

**Fig. 1:** Time course of `Bleeding` variable from study day one to five in two groups (DHF and Non-DHF).  The data are shown as raw counts (A) and proportions by group by study day (B).

\newpage

```{r rash, echo=FALSE, warning=FALSE, fig.width=10,fig.height=5}
dat$rash_f <- NA
dat$rash_f[which(dat$rash == 2)] <- "Yes"
dat$rash_f[which(dat$rash == 1)] <- "No"

cdat <- aggregate(sno ~ simple_Dx +study_day + rash_f, dat[!is.na(dat$rash_f),],FUN = length)

pdat <- aggregate(sno ~ simple_Dx +study_day , dat[!is.na(dat$rash_f),],FUN = length)
pdat <- merge(cdat,pdat, by = c("simple_Dx","study_day"))
pdat$perc <- 100*(pdat$sno.x/pdat$sno.y)

gA <- ggplot(cdat,aes(x=simple_Dx,fill = rash_f,  y = sno))+
  geom_bar(stat="identity", lwd = 1)+
  scale_fill_manual(name = "Rash", values = c("gray","gray5"))+
  xlab("")+
  ylab("Number of patients")+
  facet_grid(.~study_day)+
  theme(legend.position = "top",
        axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))

gB <-ggplot(pdat,aes(x=simple_Dx,fill = rash_f,  y = perc))+
  geom_bar(stat="identity", lwd = 1)+
  scale_fill_manual(name = "Rash", values = c("gray","gray5"))+
  xlab("")+
  ylab("Proportion of patients (%)")+
  facet_grid(.~study_day)+
  theme(legend.position = "top",
        axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))

g <- ggarrange(gA,gB,ncol = 2,nrow = 1, labels = c("A","B"))
print(g)
ggsave(plot = g, filename = "../Plots/Supplement_rash.eps",width=10,height = 5,units = "in", device=cairo_ps)
```

**Fig. 2:** Time course of `Rash` variable from study day one to five in two groups (DHF and Non-DHF).  The data are shown as raw counts (A) and proportions by group by study day (B).

\newpage

```{r bruising, echo=FALSE, warning=FALSE, fig.width=10,fig.height=5}
dat$bruising_f <- NA
dat$bruising_f[which(dat$bruising == 2)] <- "Yes"
dat$bruising_f[which(dat$bruising == 1)] <- "No"

cdat <- aggregate(sno ~ simple_Dx +study_day + bruising_f, dat[!is.na(dat$bruising_f),],FUN = length)

pdat <- aggregate(sno ~ simple_Dx +study_day , dat[!is.na(dat$bruising_f),],FUN = length)
pdat <- merge(cdat,pdat, by = c("simple_Dx","study_day"))
pdat$perc <- 100*(pdat$sno.x/pdat$sno.y)

gA <- ggplot(cdat,aes(x=simple_Dx,fill = bruising_f,  y = sno))+
  geom_bar(stat="identity", lwd = 1)+
  scale_fill_manual(name = "Bruising", values = c("gray","gray5"))+
  xlab("")+
  ylab("Number of patients")+
  facet_grid(.~study_day)+
  theme(legend.position = "top",
        axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))

gB <-ggplot(pdat,aes(x=simple_Dx,fill = bruising_f,  y = perc))+
  geom_bar(stat="identity", lwd = 1)+
  scale_fill_manual(name = "Bruising", values = c("gray","gray5"))+
  xlab("")+
  ylab("Proportion of patients (%)")+
  facet_grid(.~study_day)+
  theme(legend.position = "top",
        axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))

g <- ggarrange(gA,gB,ncol = 2,nrow = 1, labels = c("A","B"))
print(g)
ggsave(plot = g, filename = "../Plots/Supplement_bruising.eps",width=10,height = 5,units = "in", device=cairo_ps)
```

**Fig. 3:** Time course of `Bruising` variable from study day one to five in two groups (DHF and Non-DHF).  The data are shown as raw counts (A) and proportions by group by study day (B).

\newpage

```{r diarrhea_d04, echo=FALSE, warning=FALSE, fig.width=10,fig.height=5}
dat$diarrhea_d04_f <- NA
dat$diarrhea_d04_f[which(dat$diarrhea_d04 == 2)] <- "Yes"
dat$diarrhea_d04_f[which(dat$diarrhea_d04 == 1)] <- "No"

cdat <- aggregate(sno ~ simple_Dx +study_day + diarrhea_d04_f, dat[!is.na(dat$diarrhea_d04_f),],FUN = length)

pdat <- aggregate(sno ~ simple_Dx +study_day , dat[!is.na(dat$diarrhea_d04_f),],FUN = length)
pdat <- merge(cdat,pdat, by = c("simple_Dx","study_day"))
pdat$perc <- 100*(pdat$sno.x/pdat$sno.y)

gA <- ggplot(cdat,aes(x=simple_Dx,fill = diarrhea_d04_f,  y = sno))+
  geom_bar(stat="identity", lwd = 1)+
  scale_fill_manual(name = "Diarrhea", values = c("gray","gray5"))+
  xlab("")+
  ylab("Number of patients")+
  facet_grid(.~study_day)+
  theme(legend.position = "top",
        axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))

gB <-ggplot(pdat,aes(x=simple_Dx,fill = diarrhea_d04_f,  y = perc))+
  geom_bar(stat="identity", lwd = 1)+
  scale_fill_manual(name = "Diarrhea", values = c("gray","gray5"))+
  xlab("")+
  ylab("Proportion of patients (%)")+
  facet_grid(.~study_day)+
  theme(legend.position = "top",
        axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))

g <- ggarrange(gA,gB,ncol = 2,nrow = 1, labels = c("A","B"))
print(g)

ggsave(plot = g, filename = "../Plots/Supplement_diarrhea.eps",width=10,height = 5,units = "in", device=cairo_ps)
```

**Fig. 4:** Time course of `Diarrhea` variable from study day one to five in two groups (DHF and Non-DHF).  The data are shown as raw counts (A) and proportions by group by study day (B).

\newpage

```{r uri_d04, echo=FALSE, warning=FALSE, fig.width=10,fig.height=5}
dat$uri_d04_f <- NA
dat$uri_d04_f[which(dat$uri_d04 == 2)] <- "Yes"
dat$uri_d04_f[which(dat$uri_d04 == 1)] <- "No"

cdat <- aggregate(sno ~ simple_Dx +study_day + uri_d04_f, dat[!is.na(dat$uri_d04_f),],FUN = length)

pdat <- aggregate(sno ~ simple_Dx +study_day , dat[!is.na(dat$uri_d04_f),],FUN = length)
pdat <- merge(cdat,pdat, by = c("simple_Dx","study_day"))
pdat$perc <- 100*(pdat$sno.x/pdat$sno.y)

gA <- ggplot(cdat,aes(x=simple_Dx,fill = uri_d04_f,  y = sno))+
  geom_bar(stat="identity", lwd = 1)+
  scale_fill_manual(name = "URI", values = c("gray","gray5"))+
  xlab("")+
  ylab("Number of patients")+
  facet_grid(.~study_day)+
  theme(legend.position = "top",
        axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))

gB <-ggplot(pdat,aes(x=simple_Dx,fill = uri_d04_f,  y = perc))+
  geom_bar(stat="identity", lwd = 1)+
  scale_fill_manual(name = "URI", values = c("gray","gray5"))+
  xlab("")+
  ylab("Proportion of patients (%)")+
  facet_grid(.~study_day)+
  theme(legend.position = "top",
        axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))

g <- ggarrange(gA,gB,ncol = 2,nrow = 1, labels = c("A","B"))
print(g)

ggsave(plot = g, filename = "../Plots/Supplement_uri.eps",width=10,height = 5,units = "in", device=cairo_ps)
```

**Fig. 5:** Time course of `URI` (Upper respiratory infection) variable from study day one to five in two groups (DHF and Non-DHF).  The data are shown as raw counts (A) and proportions by group by study day (B).

\newpage

```{r abdominal_d04, echo=FALSE, warning=FALSE, fig.width=10,fig.height=5}
dat$abdominal_d04_f <- NA
dat$abdominal_d04_f[which(dat$abdominal_d04 == 2)] <- "Yes"
dat$abdominal_d04_f[which(dat$abdominal_d04 == 1)] <- "No"

cdat <- aggregate(sno ~ simple_Dx +study_day + abdominal_d04_f, dat[!is.na(dat$abdominal_d04_f),],FUN = length)

pdat <- aggregate(sno ~ simple_Dx +study_day , dat[!is.na(dat$abdominal_d04_f),],FUN = length)
pdat <- merge(cdat,pdat, by = c("simple_Dx","study_day"))
pdat$perc <- 100*(pdat$sno.x/pdat$sno.y)

gA <- ggplot(cdat,aes(x=simple_Dx,fill = abdominal_d04_f,  y = sno))+
  geom_bar(stat="identity", lwd = 1)+
  scale_fill_manual(name = "Abdominal pain", values = c("gray","gray5"))+
  xlab("")+
  ylab("Number of patients")+
  facet_grid(.~study_day)+
  theme(legend.position = "top",
        axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))

gB <-ggplot(pdat,aes(x=simple_Dx,fill = abdominal_d04_f,  y = perc))+
  geom_bar(stat="identity", lwd = 1)+
  scale_fill_manual(name = "Abdominal pain", values = c("gray","gray5"))+
  xlab("")+
  ylab("Proportion of patients (%)")+
  facet_grid(.~study_day)+
  theme(legend.position = "top",
        axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))

g <- ggarrange(gA,gB,ncol = 2,nrow = 1, labels = c("A","B"))
print(g)

ggsave(plot = g, filename = "../Plots/Supplement_ab_pain.eps",width=10,height = 5,units = "in", device=cairo_ps)
```

**Fig. 6:** Time course of `Abdominal pain` variable from study day one to five in two groups (DHF and Non-DHF).  The data are shown as raw counts (A) and proportions by group by study day (B).

\newpage

```{r dyspnea, echo=FALSE, warning=FALSE, fig.width=10,fig.height=5}
dat$dyspnea_f <- NA
dat$dyspnea_f[which(dat$dyspnea == 2)] <- "Yes"
dat$dyspnea_f[which(dat$dyspnea == 1)] <- "No"

cdat <- aggregate(sno ~ simple_Dx +study_day + dyspnea_f, dat[!is.na(dat$dyspnea_f),],FUN = length)

pdat <- aggregate(sno ~ simple_Dx +study_day , dat[!is.na(dat$dyspnea_f),],FUN = length)
pdat <- merge(cdat,pdat, by = c("simple_Dx","study_day"))
pdat$perc <- 100*(pdat$sno.x/pdat$sno.y)

gA <- ggplot(cdat,aes(x=simple_Dx,fill = dyspnea_f,  y = sno))+
  geom_bar(stat="identity", lwd = 1)+
  scale_fill_manual(name = "Dyspnea", values = c("gray","gray5"))+
  xlab("")+
  ylab("Number of patients")+
  facet_grid(.~study_day)+
  theme(legend.position = "top",
        axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))

gB <-ggplot(pdat,aes(x=simple_Dx,fill = dyspnea_f,  y = perc))+
  geom_bar(stat="identity", lwd = 1)+
  scale_fill_manual(name = "Dyspnea", values = c("gray","gray5"))+
  xlab("")+
  ylab("Proportion of patients (%)")+
  facet_grid(.~study_day)+
  theme(legend.position = "top",
        axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))

g <- ggarrange(gA,gB,ncol = 2,nrow = 1, labels = c("A","B"))
print(g)

ggsave(plot = g, filename = "../Plots/Supplement_dyspnea.eps",width=10,height = 5,units = "in", device=cairo_ps)
```

**Fig. 7:** Time course of `Dyspnea` variable from study day one to five in two groups (DHF and Non-DHF).  The data are shown as raw counts (A) and proportions by group by study day (B).

\newpage

```{r liver, echo=FALSE, warning=FALSE, fig.width=10,fig.height=5}
dat$liver_f <- NA
dat$liver_f[which(dat$liver == 2)] <- "Yes"
dat$liver_f[which(dat$liver == 1)] <- "No"

cdat <- aggregate(sno ~ simple_Dx +study_day + liver_f, dat[!is.na(dat$liver_f),],FUN = length)

pdat <- aggregate(sno ~ simple_Dx +study_day , dat[!is.na(dat$liver_f),],FUN = length)
pdat <- merge(cdat,pdat, by = c("simple_Dx","study_day"))
pdat$perc <- 100*(pdat$sno.x/pdat$sno.y)

gA <- ggplot(cdat,aes(x=simple_Dx,fill = liver_f,  y = sno))+
  geom_bar(stat="identity", lwd = 1)+
  scale_fill_manual(name = "Liver tenderness", values = c("gray","gray5"))+
  xlab("")+
  ylab("Number of patients")+
  facet_grid(.~study_day)+
  theme(legend.position = "top",
        axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))

gB <-ggplot(pdat,aes(x=simple_Dx,fill = liver_f,  y = perc))+
  geom_bar(stat="identity", lwd = 1)+
  scale_fill_manual(name = "Liver tenderness", values = c("gray","gray5"))+
  xlab("")+
  ylab("Proportion of patients (%)")+
  facet_grid(.~study_day)+
  theme(legend.position = "top",
        axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))

g <- ggarrange(gA,gB,ncol = 2,nrow = 1, labels = c("A","B"))
print(g)

ggsave(plot = g, filename = "../Plots/Supplement_liver_tenderness.eps",width=10,height = 5,units = "in", device=cairo_ps)
```

**Fig. 8:** Time course of `Liver tenderness` variable from study day one to five in two groups (DHF and Non-DHF).  The data are shown as raw counts (A) and proportions by group by study day (B).

\newpage


```{r lymph, echo=FALSE, warning=FALSE, fig.width=10,fig.height=5}
dat$lymph_f <- NA
dat$lymph_f[which(dat$lymph == 2)] <- "Yes"
dat$lymph_f[which(dat$lymph == 1)] <- "No"

cdat <- aggregate(sno ~ simple_Dx +study_day + lymph_f, dat[!is.na(dat$lymph_f),],FUN = length)

pdat <- aggregate(sno ~ simple_Dx +study_day , dat[!is.na(dat$lymph_f),],FUN = length)
pdat <- merge(cdat,pdat, by = c("simple_Dx","study_day"))
pdat$perc <- 100*(pdat$sno.x/pdat$sno.y)

gA <- ggplot(cdat,aes(x=simple_Dx,fill = lymph_f,  y = sno))+
  geom_bar(stat="identity", lwd = 1)+
  scale_fill_manual(name = "Lymph nodes enlargement", values = c("gray","gray5"))+
  xlab("")+
  ylab("Number of patients")+
  facet_grid(.~study_day)+
  theme(legend.position = "top",
        axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))

gB <-ggplot(pdat,aes(x=simple_Dx,fill = lymph_f,  y = perc))+
  geom_bar(stat="identity", lwd = 1)+
  scale_fill_manual(name = "Lymph nodes enlargement", values = c("gray","gray5"))+
  xlab("")+
  ylab("Proportion of patients (%)")+
  facet_grid(.~study_day)+
  theme(legend.position = "top",
        axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))

g <- ggarrange(gA,gB,ncol = 2,nrow = 1, labels = c("A","B"))
print(g)

ggsave(plot = g, filename = "../Plots/Supplement_lymph_enlarge.eps",width=10,height = 5,units = "in", device=cairo_ps)
```

**Fig. 9:** Time course of `Lymph nodes enlargement` variable from study day one to five in two groups (DHF and Non-DHF).  The data are shown as raw counts (A) and proportions by group by study day (B).

\newpage

```{r injected, echo=FALSE, warning=FALSE, fig.width=10,fig.height=5}
dat$injected_f <- NA
dat$injected_f[which(dat$injected == 2)] <- "Yes"
dat$injected_f[which(dat$injected == 1)] <- "No"

cdat <- aggregate(sno ~ simple_Dx +study_day + injected_f, dat[!is.na(dat$injected_f),],FUN = length)

pdat <- aggregate(sno ~ simple_Dx +study_day , dat[!is.na(dat$injected_f),],FUN = length)
pdat <- merge(cdat,pdat, by = c("simple_Dx","study_day"))
pdat$perc <- 100*(pdat$sno.x/pdat$sno.y)

gA <- ggplot(cdat,aes(x=simple_Dx,fill = injected_f,  y = sno))+
  geom_bar(stat="identity", lwd = 1)+
  scale_fill_manual(name = "Injected conjunctiva", values = c("gray","gray5"))+
  xlab("")+
  ylab("Number of patients")+
  facet_grid(.~study_day)+
  theme(legend.position = "top",
        axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))

gB <-ggplot(pdat,aes(x=simple_Dx,fill = injected_f,  y = perc))+
  geom_bar(stat="identity", lwd = 1)+
  scale_fill_manual(name = "Injected conjunctiva", values = c("gray","gray5"))+
  xlab("")+
  ylab("Proportion of patients (%)")+
  facet_grid(.~study_day)+
  theme(legend.position = "top",
        axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))

g <- ggarrange(gA,gB,ncol = 2,nrow = 1, labels = c("A","B"))
print(g)

ggsave(plot = g, filename = "../Plots/Supplement_inj_conj.eps",width=10,height = 5,units = "in", device=cairo_ps)
```

**Fig. 10:** Time course of `Injected conjunctiva` variable from study day one to five in two groups (DHF and Non-DHF).  The data are shown as raw counts (A) and proportions by group by study day (B).

\newpage

```{r itching, echo=FALSE, warning=FALSE, fig.width=10,fig.height=5}
dat$itching_f <- NA
dat$itching_f[which(dat$itching == 2)] <- "Yes"
dat$itching_f[which(dat$itching == 1)] <- "No"

cdat <- aggregate(sno ~ simple_Dx +study_day + itching_f, dat[!is.na(dat$itching_f),],FUN = length)

pdat <- aggregate(sno ~ simple_Dx +study_day , dat[!is.na(dat$itching_f),],FUN = length)
pdat <- merge(cdat,pdat, by = c("simple_Dx","study_day"))
pdat$perc <- 100*(pdat$sno.x/pdat$sno.y)

gA <- ggplot(cdat,aes(x=simple_Dx,fill = itching_f,  y = sno))+
  geom_bar(stat="identity", lwd = 1)+
  scale_fill_manual(name = "Itching", values = c("gray","gray5"))+
  xlab("")+
  ylab("Number of patients")+
  facet_grid(.~study_day)+
  theme(legend.position = "top",
        axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))

gB <-ggplot(pdat,aes(x=simple_Dx,fill = itching_f,  y = perc))+
  geom_bar(stat="identity", lwd = 1)+
  scale_fill_manual(name = "Itching", values = c("gray","gray5"))+
  xlab("")+
  ylab("Proportion of patients (%)")+
  facet_grid(.~study_day)+
  theme(legend.position = "top",
        axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))

g <- ggarrange(gA,gB,ncol = 2,nrow = 1, labels = c("A","B"))
print(g)

ggsave(plot = g, filename = "../Plots/Supplement_itch.eps",width=10,height = 5,units = "in", device=cairo_ps)
```

**Fig. 11:** Time course of `Itching` variable from study day one to five in two groups (DHF and Non-DHF).  The data are shown as raw counts (A) and proportions by group by study day (B).

\newpage